The Future of Cybersecurity Education and Accreditation: A Case Study of the UK

### 2019-06-22 FIE2019-final-TPJHD.tex
Some reorganisation

% this section feels someone disjoint from what we have written so far...
To illustrate some of these challenges, four examples are briefly explored: the European Union's General Data Protection Regulation (GDPR); Agile development; one industry sector (with rigorous demands for secure software); and impact of these cases upon one another.

@@

\subsection{Research Questions}
There are various levels of specialism at which cybersecurity education can be addressed.
\begin{enumerate}
\item The general public --- this is important, but there are many initiatives in this area (e.g. Cyber Essentials\footnote{Cyber Essentials is a UK Government-backed, industry-supported scheme to help organisations protect themselves against common online threats: \url{https://www.cyberessentials.ncsc.gov.uk}}, which are, rightly, largely separated from computing education.
% ({\emph{interesting point from a public engagement/science communication perspective -- aren't ``we'' trying to create a digitally competent and capable citizenry? Minor point but maybe worth mentioning e.g. being safe online, accessing public services, etc}})
%\item[JHD]This is important, agreed, but I think this is being a user: think car driving rather than car design. BUT the point I heard from the WC Engineers ``how can security be an option --- safety certainly isn't'' is also relevant.
\item The general computer science graduate.
\item The generalist computer science masters graduate.
\item The specialist computer science graduate.
\item The specialist computer science masters graduate.
\end{enumerate}
The focus of this paper is on 2-3: the general Computer Science graduate.
\begin{description}
\item[RQ1]What cybersecurity is taught and what cybersecurity should be taught to the general Computer Science  students?
\item[RQ2]Should cybersecurity be taught stand-alone or in an integrated manner to general Computer Science students?
\item[RQ3]Can accreditation by professional, statutory and regulatory bodies (PSRBs) enhance the provision of cybersecurity within a body's jurisdiction?
\end{description}

@@

\subsection{Current situation}
The ACM/IEEE-CS Joint Task Force on Computing Curricula~\cite[p.~97]{ACM2013a} takes a distinct view on the Knowledge Areas (KAs) related to RQ2:
\begin{quote}
{\emph{The Information Assurance and Security KA is unique among the set of KAs presented here
given the manner in which the topics are pervasive throughout other KAs}}
\end{quote}
It proposes 9 ``core'' hours and 63.5 distributed across the other KAs.
%\pagebreak - to fix URL issues
\par
Nevertheless, the situation on the ground is different: \cite{Ackerman2019a}, describing the USA, indicates
\begin{quote}
{\emph{Universities suffer shortcomings, as well. Roughly 85 of them offer undergraduate and/or graduate degrees in cybersecurity. There is a big catch, however. Far more diversified computer science programs, which attract substantially more students, don't mandate even one cybersecurity course.}}
\end{quote}

@@

% move this section back to Intro?
\section{Policy Context}

% TC: mention NCSC
For a few years now there has been a recognised need to build knowledge, skills and capacity in the area of cybersecurity. This need has led to the establishment of a number of initiatives from a number of national governments for example The UK Cyber Security Strategy. \cite{UKCabinetOffice} or National Initiative for Cybersecurity Education (NICE) in the USA \cite{NICE}.

The teaching of cybersecurity in higher education pre-dates these initiatives and there has been recognition of the need for the inclusion of cybersecurity as part of the Computer Science discipline for a number of years \cite{Hentea2006}. There has  been a debate as to whether cybersecurity is distinct discipline from Computer Science \cite{McGettrick2013}. The consensus now is that cybersecurity is both a discipline in its own right and that cybersecurity should be taught within Computer Science and related degrees. There have been a number of international initiatives international to define curricula to support this for example the ACM general curriculum  \cite[which added ``Information Assurance and Security'' for the first time]{ACM2013a} and specialised cybersecurity Programmes \cite{ACMIEEEAISSIGSECIFIP}.

@@

\IEEEtriggeratref{43}

>>>>

%\subsection{Policy Context}

This need to build knowledge, skills and capacity in the area of cybersecurity has led to the establishment of a number of initiatives from a number of national governments, for example the UK's Cyber Security Strategy~\cite{UKCabinetOffice} (and the setting up of the UK National Cyber Security Centre), or National Initiative for Cybersecurity Education (NICE) in the USA \cite{NICE}.

The teaching of cybersecurity in higher education pre-dates these initiatives and there has been recognition of the need for the inclusion of cybersecurity as part of the Computer Science discipline for a number of years \cite{Hentea2006}. There has been a debate as to whether cybersecurity is distinct discipline from Computer Science \cite{McGettrick2013}. The consensus now is that cybersecurity is both a discipline in its own right and that cybersecurity should be taught within Computer Science and related degrees. There have been a number of international initiatives international to define curricula to support this for example the ACM Computer Science Curricula Recommendations \cite[which added ``Information Assurance and Security'' for the first time]{ACM2013a} and specialised cybersecurity Programmes \cite{ACMIEEEAISSIGSECIFIP}.

% need a better title for this!
\subsection{Some Examples}

To illustrate some of these challenges, four examples are briefly explored: the European Union's General Data Protection Regulation (GDPR); Agile development; one industry sector (with rigorous demands for secure software); and impact of these cases upon one another.

@@

\section{Research Questions}
There are various levels of specialism at which cybersecurity education can be addressed.
\begin{enumerate}
\item The general public --- this is important, but there are many initiatives in this area (e.g. Cyber Essentials\footnote{Cyber Essentials is a UK Government-backed, industry-supported scheme to help organisations protect themselves against common online threats: \url{https://www.cyberessentials.ncsc.gov.uk}}, which are, rightly, largely separated from computing education.
% ({\emph{interesting point from a public engagement/science communication perspective -- aren't ``we'' trying to create a digitally competent and capable citizenry? Minor point but maybe worth mentioning e.g. being safe online, accessing public services, etc}})
%\item[JHD]This is important, agreed, but I think this is being a user: think car driving rather than car design. BUT the point I heard from the WC Engineers ``how can security be an option --- safety certainly isn't'' is also relevant.
\item The general computer science graduate.
\item The generalist computer science masters graduate.
\item The specialist computer science graduate.
\item The specialist computer science masters graduate.
\end{enumerate}
The focus of this paper is on 2-3: the general Computer Science graduate.
\begin{description}
\item[RQ1]What cybersecurity is taught and what cybersecurity should be taught to the general Computer Science  students?
\item[RQ2]Should cybersecurity be taught stand-alone or in an integrated manner to general Computer Science students?
\item[RQ3]Can accreditation by professional, statutory and regulatory bodies (PSRBs) enhance the provision of cybersecurity within a body's jurisdiction?
\end{description}

@@

\subsection{Current State of Play}
The ACM/IEEE-CS Joint Task Force on Computing Curricula~\cite[p.~97]{ACM2013a} takes a distinct view on the Knowledge Areas (KAs) related to RQ2:
\begin{quote}
{\emph{The Information Assurance and Security KA is unique among the set of KAs presented here
given the manner in which the topics are pervasive throughout other KAs}}
\end{quote}
It proposes 9 ``core'' hours and 63.5 distributed across the other KAs.
%\pagebreak - to fix URL issues
\par
Nevertheless, the situation on the ground is different: \cite{Ackerman2019a}, describing the USA, indicates
\begin{quote}
{\emph{Universities suffer shortcomings, as well. Roughly 85 of them offer undergraduate and/or graduate degrees in cybersecurity. There is a big catch, however. Far more diversified computer science programs, which attract substantially more students, don't mandate even one cybersecurity course.}}
\end{quote}

@@

@@

%\IEEEtriggeratref{43}
